XXX in a Tracing JIT Compiler for Efficient Dynamic Languages

### 2011-03-27 talk/icooolps2011/code/interpreter-slow.tex
Typos and typographic details.

    def change_method(self, name, value):
        self.methods[name] = value

@@

    def getattr(self, name):
	result = self.getfield(name)
	if result is None:
            result = self.cls.find_method(name)
	    if result is None:
		raise AttributeError
\end{lstlisting}

>>>>

    def write_method(self, name, value):
        self.methods[name] = value

@@

    def getattr(self, name):
	result = self.getfield(name)
	if result is None:
            result = self.cls.find_method(name)
	    if result is None:
		raise AttributeError
	return result
\end{lstlisting}
